Implementing Capon Beamforming on the GPU for Real Time Cardiac Ultrasound Imaging

### 2012-11-26 ASA2013/asa2013.tex

\title{Adapting the MVDR to a GPU for active sonar systems of different sizes.}

@@

For even larger systems we suggest employing the LCA beamformer. It does not compute a weightset, but merely computes the beamformer output for each of a predefined set of weights, and selects the one that best fulfils the MVDR criterion. The LCA creates images with a quality comparable to MVDR, and it is perfectly suited for a GPU.

\ \\
Total: 215 words (200 max)

>>>>

{\Large\bf Adapting the MVDR beamformer to a GPU for differently sized active sonar imaging systems.}

@@

For even larger systems we suggest employing the LCA beamformer. It does not calculate a weightset, but merely computes the beamformer output for each of a predefined set of weights, and selects the one that best fulfils the MVDR criterion. The LCA creates images with a quality comparable to MVDR, and it is perfectly suited for a GPU.

\ \\
Total: 192 words (200 max)

### 2012-11-26 HRUIonGPU/jrnl_article.tex

>>>>

Derivation of sliding beamspace transformation. Given a $M$ long data vector divided into $N_L$ subarrays, the beamspace transformation of the $l^{th}$ subarray is given as:
\begin{align}
x_{BS,l,k} = \frac{1}{\sqrt{L}}\sum_{p=i}^{l+L-1}x_p e^{-j2\pi k(p-l)/L} , k \in [0, N_b-1].
\end{align}
Manipulating this expression we find that
\begin{align}
x_{BS,l,k} &= \frac{1}{\sqrt{L}}((x_{BS,l-1,k} - x_{l-1})e^{-j2\pi k/L} \\ &+ x_{i+L-1}e^{-j2\pi k(L-1)/L}) \\
&= \frac{1}{\sqrt{L}}(x_{BS,l-1,k} - x_{l-1} + x_{i+L-1})e^{-j2\pi k/L}
\end{align}
For $l=0$ a full computation has to be performed.
Instructions can be saved if we utilize the overlap across subarrays. However, since the number of beams usually is small we will end up with a large memory per thread ratio ($M > N_b$). Using one GPU-thread per beam is therefore not feasible for small $N_b$ large $M$ configurations. The solution is to combine sliding with full computations. A number of thread groups target different sets of subarrays which they transform using the sliding beamspace algorithm. In that way, number of threads per sample is increased and thus the memory per thread ratio is decreased. Notice how subarrays no longer overlap after the beamspace transformation. The amount of data is increased from $M$ to $N_LN_b$ per sample. This means that we no longer can exploit spatial overlap when calculating the sample covariance matrix, but since $N_b$ is small we can now use one thread per element.

How do we calculate the number of possible subarrays $N_L$ with overlap $L-s$ in a data vector of length $M$.
\begin{align}
N_L = floor(\frac{M}{s}) - floor(\frac{L-1}{s})
\end{align}
